\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
}

}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{Mahmoud Khaled Abdelkader}}
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    +201025322746 | \href{mailto:mahmoud.abdelkader@mail.concordia.ca}{mahmoud.abdelkader@mail.concordia.ca} | 
    \href{https://sites.google.com/view/mahmoud-khaled-abdelkader}{My Portfolio}
    }
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/mahmoudkhaledabdelkader/}{mahmoud-khaled-abdelkader} | 
    \socialicon{\faGithub} \href{https://github.com/Mahmoud-khaled-A}{Mahmoud-khaled-A}
    }
\end{center}
\vspace{-6mm}
\begin{center}
    \small{Giza, Egypt}
\end{center}

\vspace{-4mm}

\section{\textbf{Summary}}
\vspace{1mm}
\small{
Dynamic Mathematics graduate with a Bachelor’s degree in Mathematics and a Master’s degree in Applied Mathematics. Skilled in Optimization and Operational Research, with a focus on strategic algorithms and decision-making processes. Experienced in teaching, mentoring, and academic presentations. Committed to community service and volunteer work.
}
\vspace{-2mm}

\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{Concordia University}{Montreal, Canada}
{PhD Student at Gina Cody School of Engineering and Computer Science }{Sep.2025 - Present}
\resumeItemListStart
\item Supervised by Dr. Yassine Yaakoubi, focusing on integrating optimisation, machine learning, and simulation to develop intelligent decision-support systems for complex real-world problems.
\resumeItemListEnd

\resumeSubheading
{Heidelberg University}{Heidelberg, Germany}
{\href{https://drive.google.com/file/d/1wFEeddLXJYCIQrGYZ8K0AeWYLAH5HXJG/view}{Visiting Scholar} }{Apr.2024 - Jun.2024}
\resumeItemListStart
\item Supervised by Dr. Michael Winckler, focusing on computational optimization for complex systems.
\resumeItemListEnd

\resumeSubheading
{University of Cape Town, African Institute for Mathematical Science (AIMS)}{Cape Town, South Africa}
{Master’s degree in Applied Mathematics}{Sep. 2023 - Jul. 2024}
\resumeItemListStart
\item Thesis: “Mathematical Modelling and Implementation of Game Strategy for the Board Game Quoridor”.
\item Relevant Coursework: Nonlinear Optimization, Game Theory, Mathematical Modeling.
\resumeItemListEnd

\resumeSubheading
{Helwan University}{Helwan, Egypt}
{Pre-Master}{Sep. 2022 -May 2023}
\resumeItemListStart
\item Courses: Functional and Numerical Analysis, Abstract Algebra, Ordinary Differential Equations, Partial Differential Equations, and Topology.
\resumeItemListEnd

\resumeSubheading
{Helwan University}{Helwan, Egypt}
{Bachelor of Science in Mathematics}{Sep. 2016 - Jul. 2020}
\resumeItemListStart
\item Gained a solid knowledge in Operational Research, Real Analysis, and Linear Algebra.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Teaching and Mentoring Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{Canadian International College "CIC"}{Cairo, Egypt}
{Assistant Lecturer (Part-Time)}{Sep. 2024 - Jul. 2025}
\resumeItemListStart
\item Courses Taught: Calculus I \& II, Linear Algebra, Probability \& Statistics.
\item Responsibilities: Prepare and deliver lectures, facilitate tutorials, and design assignments.
\resumeItemListEnd

\resumeSubheading
{El-Gazeera Higher Institute for Engineering and Technology}{Cairo, Egypt}
{Assistant Lecturer}{Sep. 2024 - Jul. 2025}
\resumeItemListStart
\item Courses Taught: Calculus I \& II \& III, Linear Algebra, Discrete Math, and Numerical Analysis.
\resumeItemListEnd

\resumeSubheading
{El-Gazeera Higher Institute for Engineering and Technology}{Cairo, Egypt}
{Teaching Assistant}{Oct. 2022 - Aug.2023}
\resumeItemListStart
\item Courses Taught: Calculus I \& II \& III, Linear Algebra, Discrete Math, and Numerical Analysis.
\resumeItemListEnd

\resumeSubheading
{Helwan University}{Helwan, Egypt}
{Teaching Assistant}{Sep. 2020 -
Apr. 2021}
\resumeItemListStart
\item Guided student projects on linear and nonlinear programming methods.
\item Mentored undergraduates in applying computational tools (Python, CPLEX) to real-world optimization problems.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}




% \section{\textbf{Publications}}
% \vspace{-0.4mm}
% \small{
% \begin{enumerate}[leftmargin=*, labelsep=0.5em, align=left, widest={[1]}, itemindent=0em, label={\textbf{[\arabic*]}]}]
%     \item[\textbf{[1]}] Fathy, E., \& Khaled Abdelkader, M. (in preparation). \textbf{A novel methodology for multilevel quadratic programming under interval-valued intuitionistic fuzzy uncertainty}. 
%     \begin{itemize}
%         \item Fuzzy-based linearization approach for hierarchical decision-making; validated with numerical simulations.
%     \end{itemize}

%     \item[\textbf{[2]}] Fathy, E., \& Khaled Abdelkader, M. (in preparation). \textbf{Optimization algorithms for multilevel solid transportation problems in a rough interval environment}. 

%     \begin{itemize}
%         \item Constraint, interactive, and fuzzy frameworks for uncertainty resolution in supply chain contexts.
%     \end{itemize}
% \end{enumerate}
% }
% \vspace{-6mm}

\section{\textbf{Conferences and Workshops}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
{\href{https://deeplearningindaba.com/2025/}{Deep Learning Indaba 2025} }{University of Rwanda, Rwanda}{17-22 Aug. 2025}{}
\resumeItemListStart
\item Presented a research poster titled "Multi-Objective Route Optimization Using Graph Neural Networks".
\resumeItemListEnd

\resumeProject
{\href{https://sites.google.com/view/indabaxegypt2025}{IndabaX Egypt 2025} }{Academy of Scientific Research and Technology (ASRT), Egypt}{1-2 Jul. 2025}{}
\resumeItemListStart
\item Coordinated and Organized IndabaX Egypt 2025.
\resumeItemListEnd

\resumeProject
{After Research-Party}{Heidelberg University, Germany}{May 2024}{}
\resumeItemListStart
\item Presented a research poster titled "Mathematical Modelling and Game Strategy for Quoridor".
\resumeItemListEnd

\resumeProject
{Siyakhula Event}{AIMS, South Africa}{Mar 2024}{}
\resumeItemListStart
\item Presented a research poster titled "Mathematical Modelling and Game Strategy for Quoridor".
\resumeItemListEnd

\resumeProject
{Linear and Nonlinear Optimization Workshop}{AIMS, South Africa}{Mar 2024}{}
\resumeItemListStart
\item Participated in a 3-week workshop focusing on linear and nonlinear optimization.
\resumeItemListEnd

\resumeProject
{\href{https://sites.google.com/view/spring-school-stellenbosch/registration?authuser=0}{Spring School "On Symmetries of Differential \& Difference Equations and Their Applications"}}{Stellenbosch, South Africa}{Oct 2023}{}
\resumeItemListStart
\item Participated in the Spring School on symmetries of differential and difference equations.
\resumeItemListEnd

\resumeProject
{\href{http://leroy.perso.math.cnrs.fr/QFRC2023/QFRC-2023.html}{Quadratic Forms, Rings and Codes}}{Laboratoire de Mathematiques de Lens, France}{Aug 2023}{}
\resumeItemListStart
\item Participated in an online conference on quadratic forms, rings, and codes.
\resumeItemListEnd

\resumeProject
{\href{https://drive.google.com/file/d/11xDh7Ywfn-CQ1OC37PS1ca1zWv8duHSZ/view}{Data Analysis using Advanced Computational Techniques}}{Amity University Kolkata, North India, Online}{Jul 2023}{}
\resumeItemListStart
\item Participated in a five-day faculty development program on data analysis.
\resumeItemListEnd

\resumeProject
{\href{https://events.math.unipd.it/CRaM/home}{Categories, Rings and Modules}}{Online}{Jan 2023}{}
\resumeItemListStart
\item Participated in a conference in honor of Alberto Facchini.
\resumeItemListEnd

\resumeProject
{\href{https://sites.google.com/view/algebra-winter-school}{Rings, Algebras, and Category Towards Coding and Computer Algebras}}{CIMPA School, Helwan University}{Dec 2022}{}
\resumeItemListStart
\item Participated in a winter school on rings, algebras, and category theory.
\resumeItemListEnd

\resumeProject
{Topology and its Applications}{Helwan University}{Jul 2019}{}
\resumeItemListStart
\item Participated in a conference on topology and its applications.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Awards and Achievements}}
\vspace{-0.4mm}
\resumeSubHeadingListStart


\resumeProject
{Fully Funded PhD’s Scholarship}{Concordia University, Canada}{Sep. 2025 - Jul. 2029}{}
\resumeItemListStart
\item Funding Source: Concordia University
\item Funding Amount: 127,463 USD
\resumeItemListEnd


\resumeProject
{Grant to Organize \href{https://sites.google.com/view/indabaxegypt2025}{IndabaX Egypt} 2025}{\href{https://deeplearningindaba.com/2025/}{Deep Learning Indaba} and \href{https://mastercardfdn.org/}{MasterCard Foundation}}{Feb 2025}{}
\resumeItemListStart
\item Funding Amount: 2000 USD
\resumeItemListEnd

\resumeProject
{\href{https://drive.google.com/file/d/1wFEeddLXJYCIQrGYZ8K0AeWYLAH5HXJG/view}{Visiting Scholar Funding}}{Heidelberg University's HGS MathComp}{Apr. 2024 - May 2024}{}
\resumeItemListStart
\item Funding Amount: 3200 EUR
\resumeItemListEnd

\resumeProject
{\href{https://drive.google.com/file/d/1Cj1eicnGzgb8cs7Li_7Yz7DgOE1Rk_vL/view}{Fully Funded Master’s Scholarship}}{Cape Town University, South Africa}{Oct. 2023 - Jul. 2024}{}
\resumeItemListStart
\item Funding Source: \href{https://drive.google.com/file/d/1Cw4_Y6gpo1ibaBJZuy6qBuG3kyzvXKQj/view}{Mastercard Foundation} and \href{https://drive.google.com/file/d/1Cj1eicnGzgb8cs7Li_7Yz7DgOE1Rk_vL/view}{AIMS}
\item Funding Amount: 9000 USD
\resumeItemListEnd

\resumeProject
{Ideal Student Competition}{Helwan University}{Dec 2019}{}
\resumeItemListStart
\item Seventh Place in the Ideal Student Competition at Helwan University.
\resumeItemListEnd

\resumeProject
{Ideal Student Certificate}{Faculty of Science, Helwan University}{Dec 2019}{}
\resumeItemListStart
\item Received the Ideal Student Certificate from the Faculty of Science.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Professional Memberships}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumePOR{\href{https://www.theorsociety.com/}{Operation Research Society}}{ Student Member}{May 2024 - Present}
\resumePOR{\href{https://drive.google.com/file/d/1u1IxL-j9GyVTEuRObLXcH8iR-3JnPC0H/view?usp=sharing}{European Mathematical Society}}{ Student Member}{Apr 2024 - Apr 2026}

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Skills}}
\vspace{-0.4mm}
\resumeHeadingSkillStart

\resumeSubItem{Programming Languages:}{\href{https://drive.google.com/file/d/1CakxGWXE1Zg6QiP_6TFMqxniJFTiJY9P/view?usp=sharing}{Python}, C++, R}
\resumeSubItem{Mathematical Software:}{CPLEX, GeoGebra, plotly}
\resumeSubItem{Data Analysis:}{R software, Microsoft Office}
\resumeSubItem{Other Tools:}{Canva, Emaze}

\resumeHeadingSkillEnd
% \vspace{-6mm}

\section{\textbf{Volunteer and Social Work}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
{Community Service}{Mastercard Foundation Scholar}{Mar 2024}{}
\resumeItemListStart
\item Engaged in educational tutoring at Muizenberg High, South Africa.
\resumeItemListEnd

\resumeProject
{\href{https://www.siyakhula.aims.ac.za/}{Siyakhula Event}}{AIMS, South Africa}{Mar 2024}{}
\resumeItemListStart
\item Volunteered to boost Africa’s mathematical sciences.
\resumeItemListEnd

\resumeProject
{CIMPA (\href{https://sites.google.com/view/algebra-winter-school}{Algebra Winter School})}{Helwan University}{Dec 2022}{}
\resumeItemListStart
\item Facilitated academic exchanges and supported workshop organization.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Personal Information}}
% \vspace{-0.4mm}
\vspace{0.2 cm}
\small{
\textbf{Date of Birth:} 22 Dec. 1997 \\
\textbf{Citizenship:} Egyptian
}
\vspace{-2mm}

\section{\textbf{References}}
\vspace{0.2cm}
\small{
\begin{enumerate}[leftmargin=*,labelsep=2mm]
\item \textbf{Prof. Susan Eldeken}\\
   Mathematics Department, Helwan University\\
   Email: \href{Sfdeken@science.helwan.edu.eg}{Sfdeken@science.helwan.edu.eg}\\

\item \textbf{Dr. Karin-Therese Howell}\\
   Academic Director, African Institute for Mathematical Science\\
   Email: \href{howell@aims.ac.za}{howell@aims.ac.za}\\

\item \textbf{Dr. Eman Fathy}\\
   Department of Mathematics, Faculty of Science, Helwan University\\
   Email: \href{eman.fathy@science.helwan.edu.eg}{eman.fathy@science.helwan.edu.eg}\\
\end{enumerate}
}

\end{document}